Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-12-27 output/paper/_figures.qmd
Nothing.

>>>>

**The figure titles and legends should be submitted as a single paragraph. The text of figure legends beyond the scale, arrow, panel locant, and axis information should not be included on the figures themselves but should be typed after the reference list. Each legend should be formatted as a separate paragraph and should include details on the place of the study, the time of the study, and the study population (if applicable). Define all figure abbreviations in the legend.**

### 2023-12-27 output/paper/_tables.qmd
Nothing.

>>>>

**Table titles should give details on the place of the study, the time of the study, and the study population (if applicable). Example, “Baseline Characteristics of Infants With Initial and Follow-up Screening, London, United Kingdom, 2001–2003.” In the table body, leave blank spaces for no entry; avoid using dashes. Order of footnotes: 1) Abbreviations: (no footnote symbol, listed alphabetically, separated by semicolons); 2) other footnotes as necessary, each preceded by a superscript lowercase letter. Footnotes must be cited in order when reading from left to right and top to bottom.**
